MLCommons Earthquake Science Benchmark

### 2022-10-16 paper-capstone-earthquake.tex
Updates from Overleaf

\PassOptionsToPackage{hyphens}{url}
\documentclass[sigplan,screen]{acmart}
\usepackage{todonotes}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage[pdf]{graphviz}
\usepackage{xpatch}
\usepackage{adjustbox}
\usepackage{makecell} 
\usepackage{ifthen}
% \usepackage[smartEllipses]{markdown}
\usepackage{comment}

@@

The data being used is the Southern California location data, between
32 to 36 lat -120 to -114 long. The data is recorded between
1950-2020. Each location point is is 0.1 by 0.1 degrees or ll km by ll
km in size or 2400 points in total. The points are then put into
spatial bag which are based on a bunch of different location points,
necessarily nearby spatially. Each location point has a time series
associated with it. The time series data holds magnitude, depth,
spatial position, and time. The data was accumulated into 2 week samples. 
\cite{fox2021earthquake}

@@

The data was filtered so only quakes with a magnitude > 3.29, or significant 
quakes, were considered. The Log Energy equation (Figure 1) was used for 
the magnitude of significant quakes inside a 2 week period. The Log Energy 
equation maximizes the largest earthquake energy values for the 2 week period. 
\cite{fox2021earthquake}

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.75\columnwidth]{images/Equations/log_energy.png}
    \caption{Log Energy \cite{fox2021earthquake}}
\end{figure}

The Energy Weighting equation (Figure 2) was used to average depth from quakes.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.75\columnwidth]{images/Equations/Q_bin.png}
    \caption{Energy Weighted \cite{fox2021earthquake}}
\end{figure}

The Multiplicity equation (Figure 3) is used to count the number of 
occurrences of significant earthquakes in a 2 week period.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.75\columnwidth]{images/Equations/Multiplicity_bin.png}
    \caption{Multiplicity \cite{fox2021earthquake}}
\end{figure}

All input values and predictions are independently normalized and have a maximum 
modulus of 1 over all space and time values. \cite{fox2022aiforscience}

@@

\TODO{Work in Progress}

Grouped faults empirically into 36 families by proximity. #Show picture of groupings. Used 4 different space filling curves to fill in empty spaces to get graph into a 2d structure.

@@

The models are measured according to two accuracy metrics, the Nash Sutcliffe Efficiency 
NSE and a visualization of predicted verse observed earthquake data. NSE measures 
the variation difference between observed and predicted data over time. $Q^t_m$ is the 
model prediction at time t, $Q^t_o$ is observed value at time t, $\overline{Q_o}$ is the 
mean observed value over all time. \cite{fox2021earthquake}

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.75\columnwidth]{images/Equations/NSE_equation.png}
    \caption{Nash Sutcliffe Efficiency \cite{fox2021earthquake}}
\end{figure}

The results are presented as the normalized NSE or NNSE. NNSE = 1/(2-NSE)
The values of NNSE ranges between 0 and 1 with 0 = mean, the higher the value the better the fit. \cite{fox2021earthquake}

@@

\begin{table*}[!ht]
\caption{Gregors MNIST Benchmarks}\label{tab:mnist}
    \centering
      \begin{adjustbox}{max width=\textwidth}
    \begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
    \hline
        Machine & real & user & sys & Driver & CUDA & GPU & \makecell{Date CPU \\released} & CPU & \makecell{Date CPU \\released} \\ \hline
        Gregors Machine & 0m11.534s & 0m13.914s & 0m05.186s & 510.47.03 & 11.6 & Gigabyte RTX3070 TI & May 31, 2021 & AMD 5950X & Nov 2020 \\ \hline
        Fox DGX & 0m19.987s & 5m12.991s & 0m49.266s & 450.142.00 & 11.0 & NVIDIA A100 80GB & & AMD EPYC 7742 64-Core & Aug 2019 \\ \hline
        Rivanna A100 & 0m29.263s & 0m14.585s & 0m7.399ss & 470.82.01 & 11.4 & NVIDIA A100-SXM4-40GB & May 14, 2020 & Intel(R) Xeon(R) CPU E5-2630 v3 @ 2.40GHz & Q3  2014 \\ \hline
        MacBook Pro & 0m31.01s & 0m25.26s & 130\% & N/A & N/A & N/A & N/A & M1 Max 66GB & Nov 2021 \\ \hline
        Rivanna P100 & 0m35.732s & 0m17.253s & 0m7.595s & 470.82.01 & 11.4 & Tesla P100-PCIE & & Intel(R) Xeon(R) CPU E5-2630 v3 @ 2.40GHz & Q3  2014 \\ \hline
        Rivanna V100 & 0m43.160s & 0m15.510s & 0m6.894s & 470.82.01 & 11.4 & Tesla V100-SXM2 & & Intel(R) Xeon(R) CPU E5-2630 v3 @ 2.40GHz & Q3  2014 \\ \hline
        Rivanna K80 & 0m57.588s & 0m20.322s & 0m9.612s & 470.82.01 & 11.4 & NVIDIA TESLA K80 & & Intel(R) Xeon(R) CPU E5-2630 v3 @ 2.40GHz & Q3  2014 \\ \hline
        Rivanna Frontend & 1m11.535s & 1m00.780s & 0m10.352s & N/A & N/A & N/A & & Intel(R) Xeon(R) CPU E5-2630 v3 @ 2.40GHz & Q3  2014 \\ \hline
        Rob K & 
    \end{tabular}
    \end{adjustbox}
\end{table*}

@@

\TODO{Rivanna description is incomplete}

UVA, Rivanna, A100, RTX3090, others may not have enough memory.
\cite{www-rivanna} \TODO{description of Rivanna on web page is not
  accurate.}

@@

@@

\begin{table*}[htb]
    \caption{Overview of compute resources.}
    \label{tab:hwoverview}
    \centering
%\begin{adjustbox}{angle=90}
\begin{adjustbox}{max width=\textwidth}
    \begin{tabular}{|r|l|ll|r|l|l|l|l|l|}
        \hline
        See also & Organization   & Machine                         & & Processors    & GPUs             & \makecell{Memory\\/Device} &  \makecell{GPU\\/Device} & \makecell{No. of\\ nodes} & Commissioned \\ 
        \hline
        \hline
         \ref{id:anl}   & ANL    & Aurora & \cite{www-aurora}         &              &                  & & & &    ??? 2022   \\ \hline
         \ref{id:ornl}  & ORNL   & Summit &\cite{www-summit}         &        27000 & \nvidia{volta}     & & & &               \\ \hline
         \ref{id:nersc} & NERSC  & Perlmutter & \cite{www-perlmutter} &         6000 & \nvidia{A100}      & & & & Jan 2022      \\ \hline
         \ref{id:sdsc}  & SDSC   & Expanse & \cite{www-expanse}       &          200 & \nvidia{V100}
         SMX2 & & & &               \\ \hline
         \ref{id:uva}   & UVA    & Rivanna &\cite{www-rivanna}       &            8 & \nvidia{A100}      & 80GB & ? & &  Feb 2022      \\
            &    &  &       &            8 & \nvidia{A100}      & 40GB & 8 & &       \\
            &    &  &       &            ? & \nvidia{RTX3090}   & 24GB & ? & ? & 2021          \\
            &    &  &       &            ? & \nvidia{K80}       & 11GB & 8 & 9 & 2021          \\
            &    &  &       &            ? & \nvidia{V100}      & 16GB & 4 & 1 & 2021          \\
            &    &  &       &            ? & \nvidia{V100}      & 32GB & 4 & 12 & 2021          \\
            &    &  &       &            ? & \nvidia{P100}      & 12GB & 4 & 3 & 2021          \\
            &    &  &       &            ? & \nvidia{RTX2080TI} & 11GB & 10 & 2 & 2021          \\
         \hline
         \ref{id:ral}   & RAL    & Pearl &\cite{www-pearl-1}         &           16 & \nvidia{V100}      & & & &  \\ \hline
         \ref{id:dgx}   & Fox    & DGX Station A100 &\cite{www-dgx-station-a100} & 4 & \nvidia{A100}      & 80GB & 4 & 1 & May 2021      \\
         \hline
    \end{tabular}
    \end{adjustbox}
\end{table*}

@@

\TODO{Add your personal computers to this table \url{https://github.com/Data-ScienceHub/mlcommons-science/issues/37}}
\begin{table*}[htb]
    \caption{Overview of compute resources.}
    \label{tab:desktops}
    \centering
%\begin{adjustbox}{angle=90}
\begin{adjustbox}{max width=\textwidth}
    \begin{tabular}{|r|l|l|l|r|r|r|l|r|l|l|l|}
        \hline
        See also & 
        Organization   & 
        Machine                         &
        OS & 
        \rot{Processors~} &
        \rot{Core~} & 
        \rot{Threads~} & 
        GPUs             & 
        \rot{\makecell{Memory\\/Device}} &  
        \rot{GPU/Device} & 
        \rot{No. of nodes~} & 
        Commissioned \\ 
        \hline
        \hline
         Table \ref{tab:gcompute}   & 
         Gregor    & 
         5950X   &  
         Ubuntu 20.04&
         1 &   
         16 & 
         32 &
         \href{https://www.gigabyte.com/Graphics-Card/GV-N307TGAMING-OC-8GD#kf}{GIGABYTE Gaming RTX 3070TI}  & 
         8GB & 
         2 &
         1 &
         Sep 2021-Feb 2022   \\
         \hline
         Table \ref{tab:gcompute}   & 
         Gregor    & 
         5950X   &  
         Ubuntu 20.04&
         1 &   
         16 & 
         32 &
         \href{https://rog.asus.com/us/graphics-cards/graphics-cards/rog-strix/rog-strix-rtx3090-o24g-gaming-model/}{ASUS ROG Strix RTX 3090} & 
         24GB & 
         & 
         & 
         Feb 2022   \\
         \hline
         \ref{sec:tcomputer}   & Thomas.A  & i7-8750H & Win11 Pro  & 1 &   ? & ? & \href{https://www.gigabyte.com/Laptop/AERO-15--RTX-20-Series#kf}{NVIDIA GeForce RTX 2070 with Max-Q Design}  & 16GB & 1 & 1 & 2019   \\
         \hline
         \ref{sec:t2computer}   & Thomas.B  & i7-7700HQ &  Win11 Pro &1 & ? & ? &  NVIDIA GeForce GTX 1060  & 16GB & 1 & 1 & 2017   \\
         \hline
         Table \ref{tab:rcompute} & 
         Rob & 
         5900HX & 
         Win11 Pro & 
         1 & 
         8 & 
         16 & 
         \href{https://rog.asus.com/us/laptops/rog-strix/2021-rog-strix-scar-15-series/}{NVidia RTX 3080} &  
         16GB & 
         1 & 
         1 & 
         11/25/2021 \\
         \hline
    \end{tabular}
    \end{adjustbox}
\end{table*}

@@

\BIOFIG{images/bio/gregor.png}{Jake Kolessar}{is a Graduate Student at
  the University of Virginia's School of Data Science. He has a
  background in mechanical engineering and 2 years of experience as a
  Modeling, Simulation and Analysis Engineer. He has supported the
  software design and development of modeling capabilities for event
  simulation products as well as the integration of models into the
  simulation framework.}

@@

@@

\begin{itemize}
    %% \item add presentation as cite,
    \item Review MLCommons \cite{www-mlcommons} 
    \item Use jabref \cite{www-jabrefg-org} for citation management
    \item Frequently check github \cite{www-mlcommons-eathquake}
    \item Read up on TFT \cite{www-onnen2021}
    \item Become familiar with the Attention Paper \cite{vaswani2017attention}
    \item Learn how to selfdeploy jupyterlab \cite{www-jupyterlab}

    \item Begin to learn about papermill \cite{www-papermill}
      \TODO{Rivanna's core configurations might be a bit limited on
        this front.  They do provide multiple versions of software
        (such as py2.7 and py3.8), but we may need to get permission
        to do something in userspace if we need to be very specific on
        a version of python.  Do we want to look into using tox,
        conda, or leave this up to the container ecosystem to solve?}

>>>>

\PassOptionsToPackage{hyphens}{url}
\documentclass[sigplan,screen]{acmart}

\usepackage{amsmath}
\usepackage{todonotes}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage[pdf]{graphviz}
\usepackage{xpatch}
\usepackage{adjustbox}
\usepackage{makecell} 
\usepackage{ifthen}
% \usepackage[smartEllipses]{markdown}
\usepackage{comment}

@@

The data being used is the Southern California location data, between
$32$ to $36$ lat $-120$ to $-114$ long. The data is recorded between
$1950-2020$. Each location point is $0.1$ by $0.1$ degrees or $11 km$ by $11
km$ in size or $2400$ points in total. The points are then put into
spatial bag which are based on a bunch of different location points,
necessarily nearby spatially. Each location point has a time series
associated with it. The time series data holds magnitude, depth,
spatial position, and time. The data was accumulated into $2$ week samples. 
\cite{fox2021earthquake}

@@

The data was filtered so only quakes with a $magnitude > 3.29$, or significant 
quakes, were considered. The Log Energy equation (\ref{eq:Log Energy}) was used for 
the magnitude of significant quakes inside a $2$ week period. The Log Energy 
equation maximizes the largest earthquake energy values for the $2$ week period
\cite{fox2021earthquake}.

    \begin{equation}
    m_{bin} = \log (Energy) = \frac{1}{1.5} \log_{10} \sum\limits^{Events}_{in\ bin} 10^{1.5m_{event}}
    \label{eq:Log Energy}
    \end{equation}

\TODO{Gregor suggests to change the event to e(1.5m) Gregor's suggestion just to show it see \ref{eq:log-energy-gregor}. possibly we should use  $in\ bin(1.5m)$ and than just $10^e$ ?. However we need to confirm.}

    \begin{equation}
    m_{bin} = \log (Energy) = \frac{1}{1.5} \log_{10} \sum\limits^{Events}_{e \in bin} 10^{e(1.5m)}
    \label{eq:log-energy-gregor}
    \end{equation}

    \begin{equation}
    m_{bin} = \log (Energy) = \frac{1}{1.5} \log_{10} \sum\limits^{Events}_{e \in bin(1.5m)} 10^e
    \label{eq:log-energy-gregor}
    \end{equation}

The Energy Weighting equation (\ref{eq:Energy Weighted}) was used to average depth from quakes \cite{fox2021earthquake}.

    \begin{equation}
    Energy\ weighted\ Quantity \ Q_{bin} = \dfrac{\sum\limits^{Events}_{in\ bin} 10^{1.5m_{event}}Q_{event}}{\sum\limits^{Events}_{in\ bin}10^{1.5m_{event}}}
    \label{eq:Energy Weighted}
    \end{equation}

The Multiplicity equation (\ref{eq:Multiplicity}) is used to count the number of 
occurrences of significant earthquakes in a 2 week period \cite{fox2021earthquake}.

    \begin{equation}
    Multiplicity_{bin} = \sum^{Events}_{in\ bin} Multiplicity_{event}
    \label{eq:Multiplicity}
    \end{equation}

All input values and predictions are independently normalized and have a maximum 
modulus of $1$ over all space and time values. \cite{fox2022aiforscience}

@@

There are hundreds of faults in the $32$ to $36$ lat $-120$ to $-114$ long area. To simplify these faults, this area was taken as a $2d$ structure spit into $2400$ individual pixels. These pixels were grouped empirically into $36$ families by proximity using $4$ different space filling curves to fill in empty spaces.

\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth]{images/Fault_groupings.png}
    \caption{Fault Regions}
\end{figure}

\subsection{Training - Test split}

From the $2400$ pixels in the $2d$ image, the $500$ most active pixels were picked. These $500$ were picked according to the magnitude > $3.29$ cut. $400$ were used for training and $100$ for validation and testing.

\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth]{images/Training_test.png}
    \caption{Training - Test Split: $400$ Training points are shown in red and $100$ test/validation points are shown in green}
\end{figure}

@@

The models are measured according to two accuracy metrics, the Nash Sutcliffe Efficiency 
($NSE$) and a visualization of predicted verse observed earthquake data. $NSE$ measures 
the variation difference between observed and predicted data over time. $Q^t_m$ is the 
model prediction at time t, $Q^t_o$ is observed value at time $t$, $\overline{Q_o}$ is the 
mean observed value over all time \cite{fox2021earthquake}.

    \begin{equation}
    NSE = 1 - \dfrac{\sum\limits^{t=T}_{t=1}(Q^t_m-Q^t_o)^2}{\sum\limits^{t=T}_{t=1}(Q^t_o-\overline{Q_o})^2}
    \label{eq:Nash Sutcliffe Efficiency}
    \end{equation}

The results are presented as the Normalized Nash Sutcliffe Efficiency ($NNSE$) \cite{fox2021earthquake}
$NNSE. NNSE = 1/(2-NSE)$
The values of $NNSE$ ranges between $0$ and $1$ with $0 = mean$, the higher the value the better the fit \cite{fox2021earthquake}.

@@

\begin{table*}[!ht]
\caption{Gregors MNIST Benchmarks}\label{tab:mnist}
    \centering
      \begin{adjustbox}{max width=\textwidth}
    \begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
    \hline
        Machine & real & user & sys & Driver & CUDA & GPU & \makecell{Date CPU \\released} & CPU & \makecell{Date CPU \\released} \\ \hline
        Gregors Machine & 0m11.534s & 0m13.914s & 0m05.186s & 510.47.03 & 11.6 & Gigabyte RTX3070 TI & May 31, 2021 & AMD 5950X & Nov 2020 \\ \hline
        Fox DGX & 0m19.987s & 5m12.991s & 0m49.266s & 450.142.00 & 11.0 & NVIDIA A100 80GB & & AMD EPYC 7742 64-Core & Aug 2019 \\ \hline
        Rivanna A100 & 0m29.263s & 0m14.585s & 0m7.399ss & 470.82.01 & 11.4 & NVIDIA A100-SXM4-40GB & May 14, 2020 & Intel(R) Xeon(R) CPU E5-2630 v3 @ 2.40GHz & Q3  2014 \\ \hline
        MacBook Pro & 0m31.01s & 0m25.26s & 130\% & N/A & N/A & N/A & N/A & M1 Max 66GB & Nov 2021 \\ \hline
        Rivanna P100 & 0m35.732s & 0m17.253s & 0m7.595s & 470.82.01 & 11.4 & Tesla P100-PCIE & & Intel(R) Xeon(R) CPU E5-2630 v3 @ 2.40GHz & Q3  2014 \\ \hline
        Rivanna V100 & 0m43.160s & 0m15.510s & 0m6.894s & 470.82.01 & 11.4 & Tesla V100-SXM2 & & Intel(R) Xeon(R) CPU E5-2630 v3 @ 2.40GHz & Q3  2014 \\ \hline
        Rivanna K80 & 0m57.588s & 0m20.322s & 0m9.612s & 470.82.01 & 11.4 & NVIDIA TESLA K80 & & Intel(R) Xeon(R) CPU E5-2630 v3 @ 2.40GHz & Q3  2014 \\ \hline
        Rivanna Frontend & 1m11.535s & 1m00.780s & 0m10.352s & N/A & N/A & N/A & & Intel(R) Xeon(R) CPU E5-2630 v3 @ 2.40GHz & Q3  2014 \\ \hline
        Rob K & \\ \hline
        Thomas AERO 15 & 0m3.387s & 0m00.000s & 0m0.015s & 511.79 & 11.6 & NVIDIA RTX 2070 & June 1, 2019 & Intel Core i7-8750H @ 2.20GHz & Q2  2018 \\ \hline
    \end{tabular}
    \end{adjustbox}
\end{table*}

@@

\TODO{Rivanna description needs review}

UVA, Rivanna, A100, RTX3090, others may not have enough memory.
\cite{www-rivanna} \TODO{Write paragraph describing Rivanna compute cluster}

@@

\section{GPU Analysis}

Sample Text about GPU Event Times

\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth]{images/GPU/event_times.png}
    \caption{GPU Event Times: Nvidia V100 2 Epoch Experiment on Rivanna localscratch}
\end{figure}

Sample Text about Epoch Validation Figure

\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth]{images/GPU/validation.png}
    \caption{Epoch Validation: Nvidia V100 2 Epoch Experiment on Rivanna localscratch}
\end{figure}

Sample Text about kWh/Epoch

\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth]{images/GPU/kWh_per_epoch.png}
    \caption{Average kWh per Epoch: }
\end{figure}

@@

\begin{table*}[htb]
    \caption{Overview of compute resources.}
    \label{tab:hwoverview}
    \centering
%\begin{adjustbox}{angle=90}
\begin{adjustbox}{max width=\textwidth}
    \begin{tabular}{|r|l|ll|r|l|l|l|l|l|}
        \hline
        See also & Organization   & Machine                         & & Processors    & GPUs             & \makecell{Memory\\/Device} &  \makecell{GPU\\/Device} & \makecell{No. of\\ nodes} & Commissioned \\ 
        \hline
        \hline
         \ref{id:anl}   & ANL    & Aurora & \cite{www-aurora}         &              &                  & & & &    ??? 2022   \\ \hline
         \ref{id:ornl}  & ORNL   & Summit &\cite{www-summit}         &        27000 & \nvidia{volta}     & & & &               \\ \hline
         \ref{id:nersc} & NERSC  & Perlmutter & \cite{www-perlmutter} &         6000 & \nvidia{A100}      & & & & Jan 2022      \\ \hline
         \ref{id:sdsc}  & SDSC   & Expanse & \cite{www-expanse}       &          200 & \nvidia{V100}
         SMX2 & & & &               \\ \hline
         \ref{id:uva}   & UVA    & Rivanna &\cite{www-rivanna}       &            8 & \nvidia{A100}      & 80GB & ? & &  Feb 2022      \\
            &    &  &       &            8 & \nvidia{A100}      & 40GB & 8 & 2 &       \\
            &    &  &       &            ? & \nvidia{RTX3090}   & 24GB & ? & ? & 2021          \\
            &    &  &       &            ? & \nvidia{K80}       & 11GB & 8 & 9 (8?) & 2021          \\
            &    &  &       &            ? & \nvidia{V100}      & 16GB & 4 & 1 & 2021          \\
            &    &  &       &            ? & \nvidia{V100}      & 32GB & 4 & 12 & 2021          \\
            &    &  &       &            ? & \nvidia{P100}      & 12GB & 4 & 3 & 2021          \\
            &    &  &       &            ? & \nvidia{RTX2080TI} & 11GB & 10 & 2 & 2021          \\
         \hline
         \ref{id:ral}   & RAL    & Pearl &\cite{www-pearl-1}         &           16 & \nvidia{V100}      & & & &  \\ \hline
         \ref{id:dgx}   & Fox    & DGX Station A100 &\cite{www-dgx-station-a100} & 4 & \nvidia{A100}      & 80GB & 4 & 1 & May 2021      \\
         \hline
    \end{tabular}
    \end{adjustbox}
\end{table*}

@@

\TODO{Add your personal computers to this table \url{https://github.com/Data-ScienceHub/mlcommons-science/issues/37}}
\begin{table*}[htb]
    \caption{Overview of compute resources.}
    \label{tab:desktops}
    \centering
%\begin{adjustbox}{angle=90}
\begin{adjustbox}{max width=\textwidth}
    \begin{tabular}{|r|l|l|l|r|r|r|l|r|l|l|l|}
        \hline
        See also & 
        Organization   & 
        Machine                         &
        OS & 
        \rot{Processors~} &
        \rot{Core~} & 
        \rot{Threads~} & 
        GPUs             & 
        \rot{\makecell{Memory\\/Device}} &  
        \rot{GPU/Device} & 
        \rot{No. of nodes~} & 
        Commissioned \\ 
        \hline
        \hline
         Table \ref{tab:gcompute}   & 
         Gregor    & 
         5950X   &  
         Ubuntu 20.04&
         1 &   
         16 & 
         32 &
         \href{https://www.gigabyte.com/Graphics-Card/GV-N307TGAMING-OC-8GD#kf}{GIGABYTE Gaming RTX 3070TI}  & 
         8GB & 
         1 &
         1 &
         Sep 2021-Feb 2022   \\
         \hline
         Table \ref{tab:gcompute}   & 
         Gregor    & 
         5950X   &  
         Ubuntu 20.04&
         1 &   
         16 & 
         32 &
         \href{https://rog.asus.com/us/graphics-cards/graphics-cards/rog-strix/rog-strix-rtx3090-o24g-gaming-model/}{ASUS ROG Strix RTX 3090} & 
         24GB & 
         1 & 
         1 & 
         Feb 2022   \\
         \hline
         \ref{sec:tcomputer}   & Thomas.A  & i7-8750H & Win10 Pro  & 1 &   6 & 12 & \href{https://www.gigabyte.com/Laptop/AERO-15--RTX-20-Series#kf}{NVIDIA GeForce RTX 2070 with Max-Q Design}  & 16GB & 1 & 1 & 2019   \\
         \hline
         \ref{sec:t2computer}   & Thomas.B  & i7-7700HQ &  Win10 Pro &1 & 4 & 8 &  NVIDIA GeForce GTX 1060  & 16GB & 1 & 1 & 2017   \\
         \hline
         Table \ref{tab:rcompute} & 
         Rob & 
         5900HX & 
         Win11 Pro & 
         1 & 
         8 & 
         16 & 
         \href{https://rog.asus.com/us/laptops/rog-strix/2021-rog-strix-scar-15-series/}{NVidia RTX 3080} &  
         16GB & 
         1 & 
         1 & 
         11/25/2021 \\
         \hline
    \end{tabular}
    \end{adjustbox}
\end{table*}

@@

\BIOFIG{images/bio/jake.jpg}{Jake Kolessar}{is a Graduate Student at
  the University of Virginia's School of Data Science. He has a
  background in mechanical engineering and 2 years of experience as a
  Modeling, Simulation and Analysis Engineer. He has supported the
  software design and development of modeling capabilities for event
  simulation products as well as the integration of models into the
  simulation framework.}

@@

\BIOFIG{images/bio/j-fox.jpg}{Judy Fox} is an Associate Professor of Data  
  Science and holds a joint appointment as Associate Professor with the
  Department of Computer Science. Her research focuses on designing
  experimental systems that enable Data Science, Machine Learning, and  the
  Internet  of  Things  applications  to  harness  the  computational
  resources  of  Cloud  and  HPC  platforms  effectively.

@@

\begin{itemize}
    %% \item add presentation as cite,
    \item Review MLCommons \cite{www-mlcommons} 
    \item Use jabref \cite{www-jabrefg-org} for citation management
    \item Frequently check github \cite{www-mlcommons-eathquake}
    \item Read up on TFT \cite{www-onnen2021}
    \item Become familiar with the Attention Paper \cite{vaswani2017attention}
